R Course Syllabus

### 2023-05-16 Bookdown Syllabus/Bookdown Syllabus.Rmd
Update bookdown syllabus and remove other version of syllabus

You have been using functions since you began working in R. `paste()`, `mutate()`, `sum()`, and even `%>%` are examples of functions. Fundamentally, a function just contains some uniform code that can be applied multiple times without typing. Theoretically you do not need to write functions, but neglecting them make your code far longer, less readable, and less easy to understand. Functions are incredibly important for repetitive or complex work.

@@

Adding numbers:
```{r l6_1_1}
# You can add numbers directly, using the Mathematical operators we discussed in Lesson 3
4 + 4

@@

# This does not save much time with 2 numbers, but what about with 25
some_numbers <- round(runif(25, 0, 100))

# With addition signs
1+31+55+78+24+78+46+65+73+74+86+3+74+31+65+51+55+45+41+21+86+44+54+62+71

@@

You can create a function (often called it *defining* the function) using the following syntax:

name_of_function <- function(arguments_of_function) {
  operations performed by function
}

@@

To prevent this from happening, you can provide default arguments. If the user of the function does not provide an value to an argument, R will use the default you've provided. Let's update mult10 so that if the user does not provide a number or vector to be multiplied, it just returns `NA`.

>>>>

You have been using functions since you began working in R. `paste()`, `mutate()`, `sum()`, and even `%>%` are examples of functions. Fundamentally, a function just contains some uniform code that can be applied multiple times without typing. Theoretically you do not need to write functions, but neglecting them makes your code far longer, less readable, and less easy to understand. Functions are incredibly important for repetitive or complex work.

@@

Adding numbers:
```{r l6_1_1_1}
# You can add numbers directly, using the Mathematical operators we discussed in Lesson 3
4 + 4

@@

# This does not save much time with 2 numbers, but what about with 25
some_numbers <- round(runif(25, 0, 100))
```

```{r l6_1_1_2, echo = FALSE}
invisible(
  addlist <- paste(some_numbers, collapse = "+")
)
```

```{r l6_1_1_3}
# With addition signs
addlist
eval(parse(text = addlist))

@@

You can create a function (often called *defining* the function) using the following syntax:

```{r l6_func_syntax}
# name_of_function <- function(arguments_of_function) {
#   operations performed by function
# }
```

@@

To prevent this from happening, you can provide default arguments. If the user of the function does not provide a value to an argument, R will use the default you've provided. Let's update mult10 so that if the user does not provide a number or vector to be multiplied, it just returns `NA`.
